Cryptographic Hash Functions

### 2019-02-24 math408/presentation/hashFunctions.tex
Finalized 408 Presentation

\begin{frame}
\frametitle{MD5 Implementation}

@@

\begin{frame}
\frametitle{Sources}
\begin{thebibliography}{}
	\beamertemplatebookbibitems
	\bibitem{Practical Cryptography Website}
	\url{http://practicalcryptography.com/hashes/md5-hash/}
	\bibitem{Tutorials Point Website}
	\url{https://www.tutorialspoint.com/cryptography/cryptography_hash_functions.htm}
	\bibitem{Cryptographic Hash Functions Explained: A Beginner's Guide}
	\url{https://komodoplatform.com/cryptographic-hash-function/}
	\bibitem{Cryptographic Hash Functions}
	\url{http://alexander.holbreich.org/cryptographic-hash-functions/}
	\bibitem{Blockgeeks Website}
	\url{https://blockgeeks.com/guides/cryptographic-hash-functions/}
\end{thebibliography}
\end{frame}

%\begin{frame}
%	\frametitle{Introduction}
%	\begin{itemize}
%		\item What is a hash function?
%		\item How do hash functions work?
%		\item Uses of hash functions
%		\item Types of hash functions
%		\item Hashing in cyber security 
%		\item Hashing vs encryption 
%		\item Hash function demonstration
%		
%	\end{itemize}
%\end{frame}

>>>>

\begin{frame}
\frametitle{MD5 Implementation}
\huge\centering{MD5 Hashing Implementation}

@@

\begin{frame}
\frametitle{Sources}
\begin{thebibliography}{}
	\beamertemplatebookbibitems
	\bibitem{Cryptographic Hash Functions Explained: A Beginner's Guide}
	Daniel. (2018, December 03). Cryptographic Hash Functions Explained: A Beginner's Guide. Retrieved from \url{https://komodoplatform.com/cryptographic-hash-function/}

	\bibitem{Tutorials Point Website}
	Tutorialspoint.com. (2019). Cryptography Hash functions. Retrieved from \url{https://www.tutorialspoint.com/cryptography/cryptography_hash_functions.htm}

	\bibitem{Practical Cryptography Website}	
	Lyons, J. (2012). MD5 Hash. Retrieved from \url{http://practicalcryptography.com/hashes/md5-hash/}

	\bibitem{Cryptographic Hash Functions}
	Holbreich, A. (2016, November 01). Cryptographic Hash Functions. Retrieved from \url{http://alexander.holbreich.org/cryptographic-hash-functions/}

	\bibitem{Blockgeeks Website}
	Mikoss, I. (2019). The In's and Outs of Cryptographic Hash Functions (Blockgeek's Guide).
	Retrieved from \url{https://blockgeeks.com/guides/cryptographic-hash-functions/}
\end{thebibliography}
\end{frame}
